\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-04-29 doc/response_2_reviews_Ecography1.txt

Reviewer: 2

Comments to the Author
The manuscript asks an interesting question - is it better to use (short) time series or space-for-time substitutions. The results make intuitive sense, but they are difficult to judge because the manuscript does not give enough details about the work. There are no details about the simulations - how many years were simulated? What spatial extent? What parameter values were used? How was the (simulated) data collected? How many replicate simulations were run (if one, why were you unable to run more than one? How are we meant to know if the results replicate?)? etc. etc. Basically, it is impossible to re-create these analyses from the description. I would strongly suggest having separate Methods and Results sections, as this makes it easier to follow the description of the work (and also helps you focus on describing the methods, and the results).

RESPONSE: Our response to Reviewer 1's similar concerns addresses many of these points. We implemented the suggestion for separate Methods and Results sections by creating separate Methods and Results subsections within each of the two case studies.

### 2020-04-30 doc/response_2_reviews_Ecography1.txt

We have completed our revision, and we thank the editor and reviewers for suggestions which (we think) have strengthened our paper. Our point-by-point responses are below; all caps "RESPONSE" indicates the start of each.

@@

My main concern with the paper is that it seems to exaggerate the importance and generality of its results. The abstract and introduction give impression that ecological forecast is tackled in very general manner. However, at the end authors study only two very simplistic (even though relavant) descriptions of ecological processes. Moreover, the set of statistical models compared is very narrow. Hence, the generality of their results is limited as well. This is not a weakness as such since with this simple example authors are able to show interesting results which are rather easily understandable. However, in my opinion the tone of the paper should be much more modest and authors should give relevant information about their simulation set up already in the abstract.

RESPONSE: 
We have rewritten the second half of the abstract to make it clear that all results come from two simple simulation studies. We also looked closely at the text in the Discussion to make sure we are not overselling our results. We think the revised version makes the limited scope of inference clear. As for the limited set of simple statistical models, that choice was intentional, as the reviewer recognizes. Because the statistical models are simple, they represent a wide variety of analogous models currently used in empirical research.

I don't like the term "space-for-time". I have not encountered such term before and for me it is not informative. Why not use species distribution model or something similar that has already an established meaning.

RESPONSE: 
In our experience, "space-for-time" is a common term. A quick search on Google Scholar shows many papers with "space-for-time" in the title or abstract, including papers cited hundreds of times. Stuart Pickett's 1989 book chapter in the Long-term Studies in Ecology, titled, "Space-for-Time Substitution as an Alternative to Long-Term Studies," has been cited almost 1300 times (Google Scholar). "Species distribution model" is a narrower term, which does not encompass other response variable, such as primary production. We wanted it to be clear that space-for-time approaches are not limited to species distribution models.

@@

In lines 150 and 152 authors use term "correlate". I know that statistical models are often called correlative models in ecology but it is typically wrong and at least impresice. Hence, I would describe in more detail how the model inference was done - maximum likelihood, Bayesian inference or least squares or what.

RESPONSE: 
We replaced "correlated" with "regressed." Details on the regression models are provided in Appendix A.

@@

Comments to the Author
The manuscript asks an interesting question - is it better to use (short) time series or space-for-time substitutions. The results make intuitive sense, but they are difficult to judge because the manuscript does not give enough details about the work. There are no details about the simulations - how many years were simulated? What spatial extent? What parameter values were used? How was the (simulated) data collected? How many replicate simulations were run (if one, why were you unable to run more than one? How are we meant to know if the results replicate?)? etc. etc. Basically, it is impossible to re-create these analyses from the description. I would strongly suggest having separate Methods and Results sections, as this makes it easier to follow the description of the work (and also helps you focus on describing the methods, and the results).

RESPONSE: 
Our response to Reviewer 1's similar concerns addresses many of these points. We implemented the suggestion for separate Methods and Results sections by creating separate Methods and Results subsections within each of the two case studies.

Beyond the writing, I think one important issue is the assumption of stationarity. My guess (and I have to guess, because we're not given this information) the spatial data is taken after the simulation has run to equilibrium. But what happens if the spatial data is taken when the climate is changing? I think that would be the important question for researchers using space-for-time with contemporary data.

RESPONSE: 
Interesting question! We modified our code for the community turnover example to study the situation in which temperature increases through the entire simulation, with no stationary period for model fitting. The key result is shown in SI Fig. 1. Qualitatively, the result is consistent: at short forecast horizons the temporal statistical model makes a better forecast while at longer forecast horizons the spatial model does better. However, as we explain in the main text (lines 260-264), the forecast from the temporal model is not as accurate, even at short forecast horizons, as in the original simulation with a stationary period for model fitting. We believe this reflects that fact that the temporal statistical model does not account for a long-term trend. Doing so might recover the same kind of information about slow processes contained in the spatial statistical model.

### 2020-04-30 doc/manuscript.tex
final small revisions

\noindent \textbf{Abstract:}   Most phenomenological, statistical models used to generate ecological forecasts take either a time-series approach, based on long-term data from one location, or a space-for-time approach, based on data describing spatial patterns across environmental gradients. However, the magnitude and even the sign of environment-response relationships detected using these two approaches often differs, leading to contrasting predictions about responses to future environmental change. Here we consider how the forecast horizon determines whether more accurate predictions come from the time-series approach, the space-for-time approach, or a combination of the two. We use two simulated case studies to show that forecasts for short and long forecast horizons need to focus on different ecological processes, which are reflected in different kinds of data. In the short-term, dynamics reflect initial conditions and fast processes such as birth and death, and the time-series approach makes the best predictions. In the long-term, dynamics reflect the additional influence of slower processes such as evolutionary and ecological selection, colonization and extinction, which the space-for-time approach can effectively capture. At intermediate time-scales, a weighted average of the two approaches shows promise. However, making this weighted model operational will require new research to predict the rate at which slow processes begin to influence dynamics.

@@

We made forecasts based on two phenomenological statistical models, each representing processes operating at different time scales. One statistical model represents the time-series or ``temporal approach.'' We regressed interannual variation in an ecological response with interannual variation in temperature at just one site. The other statistical model relies on a space-for-time substitution, which we call the ``spatial approach'' for brevity. We regressed the mean temperature on the mean of an ecological state or rate across many sites.  We compared forecasts from both statistical models to the simulated dynamics to determine how well the two approaches performed at different forecast horizons. We also assessed the potential for combining the information available in temporal and spatial patterns by using a weighted average of the forecasts from the temporal and spatial approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal approach to best predict short-term dynamics, the spatial approach to best predict long-term dynamics, while the weighted model would show potential to provide the best forecasts at transitional, intermediate time scales. The three statistical models are described in Supporting Information (Appendix \ref{models}). Computer code for both case studies is available for reviewers online (https://drive.google.com/open?id=1aju04qtQvJmZG1mcpN-6hYBZILBhDfl2) and will be archived at Zenodo upon acceptance. Instructions for running the code are in the README file in the main directory of the zip archive.

@@

The model features Lotka-Volterra competitive interactions among plants within sites that are arrayed along an elevation and temperature gradient. Composition varies along the gradient because of a trade-off between growth rate and cold tolerance: cold sites are dominated by slow-growing species that can tolerate low temperatures, while warm sites are dominated by  fast-growing species that are cold intolerant. Multiple species can coexist within sites because all species experience stronger competition from conspecifics than from heterospecifics. Sites are linked by dispersal: a specified fraction of each species' offspring leaves the site where they were produced and reaches all other sites with equal probability. We provide a more detailed description of the simulation model in SI Appendix \ref{metacomm}. Parameter values for the simulations described here in the main text are shown in Table \ref{tab:comm-turn-pars}.

We first simulated a baseline period with variable but stationary temperature, followed by a period of rapid temperature increase, and then a final period of stationary temperature. Interannual variation in temperature is the same at all sites, but mean temperature varies among sites. All sites experienced the same absolute increase in mean temperature. We focused on the biomass dynamics of one focal species that dominated the central site during the baseline period. We report results from one simulation run; results were qualitatively consistent for replicate runs.

>>>>

\noindent \textbf{Abstract:}   Most phenomenological, statistical models used to generate ecological forecasts take either a time-series approach, based on long-term data from one location, or a space-for-time approach, based on data describing spatial patterns across environmental gradients. However, the magnitude and even the sign of environment-response relationships detected using these two approaches often differs, leading to contrasting predictions about responses to future environmental change. Here we consider how the forecast horizon determines whether more accurate predictions come from the time-series approach, the space-for-time approach, or a combination of the two. We use simulated case studies to show that forecasts for short and long forecast horizons need to focus on different ecological processes, which are reflected in different kinds of data. First, we simulated population or community dynamics under stationary temperature using two simple, mechanistic models. Second, we fit statistical models to the simulated data using a time-series approach, a space-for-time approach, or a weighted average. We then forecast the response to a temperature increase using the statistical models, and compared these forecasts to temperature effects simulated by the mechanistic models. We found that the time-series approach made accurate short-term predictions because it captured initial conditions and effects of fast processes such as birth and death. The space-for-time approach made more accurate long-term predictions because it better captured the influence of slower processes such as evolutionary and ecological selection. The weighted average made accurate predictions at all time scales, including intermediate time-scales where the other two approaches performed poorly. A weighted average of time-series and space-for-time approaches shows promise, but making this weighted model operational will require new research to predict the rate at which slow processes begin to influence dynamics.

@@

We made forecasts based on two phenomenological statistical models, each representing processes operating at different time scales. One statistical model represents the time-series or ``temporal approach.'' We regressed interannual variation in an ecological response on interannual variation in temperature at just one site. The other statistical model relies on a space-for-time substitution, which we call the ``spatial approach'' for brevity. We regressed the mean temperature on the mean of an ecological state or rate across many sites.  We compared forecasts from both statistical models to the simulated dynamics to determine how well the two approaches performed at different forecast horizons. We also assessed the potential for combining the information available in temporal and spatial patterns by using a weighted average of the forecasts from the temporal and spatial approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal approach to best predict short-term dynamics, the spatial approach to best predict long-term dynamics, while the weighted model would show potential to provide the best forecasts at transitional, intermediate time scales. The three statistical models are described in Supporting Information (Appendix \ref{models}). Computer code for both case studies is available for reviewers online (https://drive.google.com/open?id=1aju04qtQvJmZG1mcpN-6hYBZILBhDfl2) and will be archived at Zenodo upon acceptance. Instructions for running the code are in the README file in the main directory of the zip archive.

@@

The model features Lotka-Volterra competitive interactions among plants within sites that are arrayed along an elevation and temperature gradient. Composition varies along the gradient because of a trade-off between growth rate and cold tolerance: cold sites are dominated by slow-growing species that can tolerate low temperatures, while warm sites are dominated by  fast-growing species that are cold intolerant. Multiple species can coexist within sites because all species experience stronger competition from conspecifics than from heterospecifics. Sites are linked by dispersal: a specified fraction of each species' offspring leaves the site where they were produced and reaches all other sites with equal probability. We provide a more detailed description of the simulation model in SI Appendix \ref{metacomm}.

We first simulated a baseline period with variable but stationary temperature, followed by a period of rapid temperature increase, and then a final period of stationary temperature. Interannual variation in temperature is the same at all sites, but mean temperature varies among sites. All sites experienced the same absolute increase in mean temperature. We focused on the biomass dynamics of one focal species that dominated the central site during the baseline period. Parameter values for the simulations described in the main text are shown in Table \ref{tab:comm-turn-pars}. We report results from one simulation run; results were qualitatively consistent for replicate runs.
